Time Series Bootstrapping For Solar Current

### 2021-12-16 deliverables/paper.Rmd
Some bug/formatting fixes

```{r unfiltered-hist, fig.cap = "Distribution of power outputs before filtering low-irradiance hours.", echo=FALSE}
unfiltered_power_hist <- ggplot() +
  geom_histogram(aes(x = df$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(unfiltered_power_hist)
```

```{r filtered-hist, fig.cap = "Distribution of power outputs after filtering low-irradiance hours.", echo=FALSE}
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(filtered_power_hist)
```

@@

```{r vis, echo=FALSE}
vis_df <- rbind(boot_block_df, boot_iid_df)

>>>>

```{r unfiltered-hist, fig.cap = "Distribution of power outputs before filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
unfiltered_power_hist <- ggplot() +
  geom_histogram(aes(x = df$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(unfiltered_power_hist)
```

```{r filtered-hist, fig.cap = "Distribution of power outputs after filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..)) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(filtered_power_hist)
```

@@

```{r vis, echo=FALSE, warning=FALSE}
vis_df <- rbind(boot_block_df, boot_iid_df)
